Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/ideas-v1.tex
Added security classes to ideas

The security principals in our account of stack safety are function
activations: at any given time, pending activations
have security requirements that are recorded in a call stack, and the current
activation tracks context information that will inform its requirements when
it makes a call. Each activation has a {\it view}
of the system that maps each state element to a {\it security class}:
it may be private to an inactive principal (\(\sealed\)),
in an allocated object that is accessible to the current principal (\(\object\)),
available to be allocated (\(\unsealed\)), or
always accessible (\(\public\)).

@@

Putting these ideas together, we get the basic structure of a property in our model.
First we define the security-relevant operations that we support, a security context,
and the function according to which the security context updates with each step.
Then, we define a predicate on states and contexts that expresses the requirements
for our security property, using variants, assertions about future states, and comparison
of event traces. Finally, in order to apply the property to a specific machine, we
must determine how the machine's execution translates into security relevant operations.

>>>>

The security principals in our account of stack safety are function
activations: the context tracks, for the active function and all pending
functions, their {\em view} of the security state of the system.

\paragraph*{Views}

The security context consists of a stack of views: functions that map
each state element to a {\it security class}. The security classes are
\(\public\), \(\unsealed\), \(\object\), and \(\sealed\).

State elements that are outside of the stack---general-purpose memory used for
globals and the heap, as well as the code region and globally-relevant
registers---are always labeled \(\public\). We place security requirements on some
\(\public\) elements for purposes of \(\wbcf\), and a given enforcement mechanism
might restrict their access (e.g., by rendering code immutable) but for integrity
and confidentiality purposes they are considered accessible at all times.

For a newly active function, every element that is available for use but uninitialized
is seen as \(\unsealed\). From the perspective of the caller, the callee has no obligations
regarding its use of \(\unsealed\) elements, but the callee itself

Arguments are seen as \(\object\), meaning that their contents may be safely used.
When the active function allocates memory, that memory will also be \(\object\).
Then, on a call, \(\object\) elements that are not being used to communicate with
the new callee will become \(\sealed\)---reserved for an inactive principal,
and expected to be unchanged when it becomes active again.

@@

Putting these ideas together, we get the basic structure of a property in our model.
First we define the security-relevant operations that we support, a security context,
and the function according to which the security context updates with each step.
The security context gives each function activation a view, mapping each element to a
security class.

Then, we define our security requirements in terms of the security classes of state
elements. These take the form of predicates on states and contexts that use variants,
assertions about future return states, and comparison of event traces to capture the
desired behavior without reference to implementation details.

Separately, in order to apply a property to a specific machine, we do need to consider
implementation details, by determining how the machine's execution translates into
security relevant operations. But this step is transparent to the properties themselves.
